---
title: "DWH Project"
author: "Varshini Yanamandra"
date: "2023-04-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(httr)
library(curl)
library(jsonlite)
library(RCurl)
library(ggplot2)
library(tidytext)
library(textdata)
library(stringr)
```

ANALYSIS OF A FEW MARVEL AND DC MOVIES USING IMDB DATA

This section gets information from the OMDB API for 5 film series each from the Marvel Comic Universe and the DC universe. The film series chosen are:

Marvel Comic Universe:
1. Captain America
2. Iron Man
3. Thor
4. Spider-Man
5. The Hulk

DC:
1. Wonder Woman
2. Batman (The Dark Knight Trilogy)
3. Superman
4. Aquaman
5. Shazam!

The data is collected for the movies that have been released, as of date.

```{r}
# Getting IMDb movie IDs from the IMDb websites. This was done manually.
# The IDs of films belonging to separate film series are put in separate lists.

# MARVEL
capt.america <- c("tt0458339", "tt1843866", "tt3498820")
iron.man <- c("tt0371746", "tt1228705", "tt1300854")
thor <- c("tt0800369", "tt1981115", "tt3501632", "tt10648342")
spiderman <- c("tt0145487", "tt0316654", "tt0413300", "tt2250912", "tt6320628", "tt10872600")
hulk <- c("tt0286716", "tt0800080")

# DC
wonder.woman <- c("tt0451279", "tt7126948")
batman.dkt <- c("tt0372784", "tt0468569", "tt1345836") # The Dark Knight Trilogy
superman <- c("tt0348150", "tt0770828")
aquaman <- c("tt1477834") #, "tt9663764")
shazam <- c("tt0448115", "tt10151854")
```

Once we have the IMDb movie IDs for the movies, we use the OMDB API to extract whatever information is available for each film. An API key was obtained for the OMDB API through their website (www.omdbapi.com). This API key has been used to make requests to the API.

```{r}
# API key obtained through the website
mykey = "4ce5d1e6"
# The base URL to access the API and make requests to it
baseurl <- "http://www.omdbapi.com"

# joining the movies by comic universe to create 
# comprehensive lists for all the selected Marvel and DC films
marvel <- c(capt.america, iron.man, thor, spiderman, hulk)
dc <- c(wonder.woman, batman.dkt, superman, aquaman, shazam)

# getting API response for all Marvel films
Marvel <- rep("", length(marvel))
for (i in 1:length(marvel)) {
  Marvel[i] <- getForm(uri = baseurl, apikey = mykey, i = marvel[i])
}
# getting API response for all DC films
DC <- rep("", length(dc))
for (i in 1:length(dc)) {
  DC[i] <- getForm(uri = baseurl, apikey = mykey, i = dc[i])
}
```

```{r}
# creating summary dataframes

## the response received from the API is in the form of JSON objects
## we use fromJSON() to parse the JSON objects and convert these responses into named lists

## we start off by creating an empty dataframe with 0 rows and 
## number of columns equal to the number of keys in the JSON response
marvel.summary <- data.frame(matrix(ncol = 25, nrow = 0)) # fromJSON() response has 25 attributes
colnames(marvel.summary) <- Marvel[1] %>% fromJSON() %>% names() # getting the names from the named lists

## populating the Marvel dataframe with information from the API
for (i in 1:length(Marvel)) {
  ## this line of code puts the JSON response into the form of a dataframe row
  marvel.summary.temp <- do.call("cbind", fromJSON(Marvel[i]))
  ## binding the information on the current movie with all the movies we have so far
  marvel.summary <- rbind(marvel.summary, marvel.summary.temp)
}

marvel.summary %>% head() # need to pivot wider
marvel.summary <- pivot_wider(marvel.summary, names_from = Ratings.Source, values_from = Ratings.Value)
marvel.summary %>% head()

dc.summary <- data.frame(matrix(ncol = 25, nrow = 0))
colnames(dc.summary) <- DC[1] %>% fromJSON() %>% names()

for (i in 1:length(DC)) {
  dc.summary.temp <- do.call("cbind", fromJSON(DC[i]))
  dc.summary <- rbind(dc.summary, dc.summary.temp)
}

dc.summary %>% head() # need to pivot wider
dc.summary <- pivot_wider(dc.summary, names_from = Ratings.Source, values_from = Ratings.Value)
dc.summary %>% head()
```

```{r}
# DATA PROCESSING

# adding a new column to both the dataframes
marvel.summary$Universe <- rep("Marvel", dim(marvel.summary)[1])
dc.summary$Universe <- rep("DC", dim(dc.summary)[1])

# combining the two dataframes into one
movies <- rbind(marvel.summary, dc.summary)

l = dim(movies)[1]
movies.wins <- rep("", l)
movies.noms <- rep("", l)
movies.Owins <- rep("", l)
movies.Onoms <- rep("", l)

for (i in 1:l) {
  movies.wins[i] = str_extract(str_extract(movies$Awards[i], "[0-9]+ win"), "[0-9]+") # extract number of wins
  movies.noms[i] = str_extract(str_extract(movies$Awards[i], "[0-9]+ nomination"), "[0-9]+") # extract number of nominations
  movies.Onoms[i] = str_extract(str_extract(movies$Awards[i], "Nominated for [0-9]+ Oscar"), "[0-9]+") # extract number of Oscar nominations
  movies.Owins[i] = str_extract(str_extract(movies$Awards[i], "Won [0-9]+ Oscar"), "[0-9]+") # extract number of Oscar wins
}

movies$Wins = movies.wins
movies$Nominations = movies.noms
movies$OscarWins = movies.Owins
movies$OscarNominations = movies.Onoms
# some more processing
movies$imdbVotes <- gsub(",", "", movies$imdbVotes)
movies$BoxOffice <- gsub(",", "", movies$BoxOffice)
movies$BoxOffice <- gsub("[$]", "", movies$BoxOffice)
movies$Runtime <- gsub(" min", "", movies$Runtime)
movies$`Internet Movie Database` <- gsub("/10", "", movies$`Internet Movie Database`)
movies$`Rotten Tomatoes` <- gsub("[%]", "", movies$`Rotten Tomatoes`)
movies$Metacritic <- gsub("/100", "", movies$Metacritic)

# replacing 'NA' with 0 and converting the columns to numeric types
movies <- movies %>% mutate_at(c(5, 15:17, 21, 25:27, 29:32), ~replace_na(., "0")) %>% mutate_at(c(5, 15:17, 21, 25:27, 29:32), as.numeric)
movies %>% head()

# some cells where the numeric field values were "N/A" will be coerced to NA when using as.numeric() - this is ok, since they are null values originally. None of the numeric values are being lost.
```

```{r}
# selecting only the columns needed for further analysis
movies <- movies[, c(1, 5, 10, 16:17, 21, 26:32)]
head(movies, 3)
```

```{r}
ggplot(movies, aes(Runtime, reorder(Title, Runtime), fill = Universe)) +
  geom_col() + labs(y = "Movie")
```

From this plot, we can see that most DC movies have a longer runtime when compared to Marvel movies, in the 10 movie series we have chosen. We also see that in the DC universe movies, the 'Shazam!' films have the lowest runtimes.

```{r}
par(mfrow = c(2, 2))

ggplot(movies, aes(imdbRating, reorder(Title, imdbRating), fill = Universe)) +
  geom_col() + labs(y = "Movie") + ggtitle("IMDb Ratings")

ggplot(movies, aes(`Rotten Tomatoes`, reorder(Title, `Rotten Tomatoes`), fill = Universe)) +
  geom_col() + labs(y = "Movie") + ggtitle("Rotten Tomatoes Ratings")

ggplot(movies, aes(Metacritic, reorder(Title, Metacritic), fill = Universe)) +
  geom_col() + labs(y = "Movie") + ggtitle("Metacritic Score")
```

Based on these 3 ratings, we can't say that movies of one Universe do better than another!

```{r}
# let us take the Spiderman series and check some results out
spidey <- filter(movies, grepl("Spider-Man", Title))
spidey # these are in order of their release dates

# let us compare the Metacritic ratings with the runtime
ggplot(spidey) +
  geom_line(mapping = aes(Title, Metacritic, group = 1, color = "Metacritic Rating")) + geom_point(mapping = aes(Title, Metacritic, group = 1, color = "Metacritic Rating")) + geom_line(mapping = aes(Title, Runtime, group = 1, color = "Runtime")) + geom_point(mapping = aes(Title, Runtime, group = 1, color = "Runtime")) + theme(axis.text.x = element_text(angle = 90))
```

Interestingly, we see that the Metacritic ratings generally go down with increasing runtimes and vice-versa. This is not strictly the case, however! Spider-Man 2 is also the highest-rated movie of the series, based on Metacritic ratings.

```{r}
# let us compare wins and nominations
ggplot(spidey) +
  geom_line(aes(Title, Nominations, group = 1, color = "Nominations")) + geom_point(aes(Title, Nominations, group = 1, color = "Nominations")) + geom_line(aes(Title, Wins, group = 1, color = "Wins")) + geom_point(aes(Title, Wins, group = 1, color = "Wins")) + geom_line(aes(Title, OscarNominations, group = 1, color = "Oscar Nominations")) + geom_point(aes(Title, OscarNominations, group = 1, color = "Oscar Nominations")) + geom_line(aes(Title, OscarWins, group = 1, color = "Oscar Wins")) + geom_point(aes(Title, OscarWins, group = 1, color = "Oscar Wins")) + theme(axis.text.x = element_text(angle = 90))
```

Spider-Man: Homecoming seems to have done the worst in terms of both wins and nominations for awards, while the next movie, Spider-Man: No Way Home did the best. However, Spider-Man 2 seems to have an Oscar win without an Oscar nomination, which is not possible! On doing an internet search, the film actually received 3 Oscar nominations, making it both the film in the series with the highest Oscar nominations and wins. This is due to the way we extracted the information using Regular Expressions. The description from OMDB only said "Won 1 Oscar."

```{r}
ggplot(movies, aes(imdbVotes, reorder(Title, imdbVotes), fill = Universe)) +
  geom_col() + labs(y = "Movie") + ggtitle("IMDb Votes")
```

The top 3 movies based on votes are all DC movies, and are also all Batman movies. The difference between the number of votes for the movies at place 3 (Batman Begins) and place 4 (Iron Man) is huge!

```{r}
# sentiment analysis using the NRC lexicon
bing <- get_sentiments("bing")
names(movies)

plots <- movies[, c(1, 3, 9)]
plots <- plots %>% unnest_tokens(word, Plot) %>% inner_join(bing)
plots <- plots %>% count(Universe, sentiment)

p1 <- plots %>% filter(Universe == "DC")
word_sum_dc = sum(p1$n)
p1 <- plots %>% filter(Universe == "Marvel")
word_sum_marvel = sum(p1$n)
plots <- plots %>% mutate(prop_sentiment = n/word_sum_dc)
plots$prop_sentiment[3:4] <- plots$n[3:4]/word_sum_marvel

plots

ggplot(plots, aes(x = prop_sentiment, y = reorder(sentiment, prop_sentiment), fill = Universe)) +
  geom_bar(stat = "identity", position = "dodge") + xlab("Proportion of sentiment") + ylab("Sentiment")
```

We can see that there is a very high proportion of negative sentiments when compared to positive sentiments for both the universes. DC seems to have a higher proportion of positive sentiment in their plots, generally, when compared to Marvel. To get more clarity, let us use the nrc lexicon for a detailed analysis of the sentiments. 

```{r}
nrc <- get_sentiments("nrc")

plots <- movies[, c(1, 3, 9)]
plots <- plots %>% unnest_tokens(word, Plot) %>% inner_join(nrc)
plots <- plots %>% count(Universe, sentiment)
plots <- plots %>% filter(sentiment != "positive", sentiment != "negative")

p1 <- plots %>% filter(Universe == "DC")
word_sum_dc = sum(p1$n)
p1 <- plots %>% filter(Universe == "Marvel")
word_sum_marvel = sum(p1$n)
plots <- plots %>% mutate(prop_sentiment = n/word_sum_dc)
plots$prop_sentiment[9:16] <- plots$n[9:16]/word_sum_marvel

ggplot(plots, aes(x = prop_sentiment, y = reorder(sentiment, prop_sentiment), fill = Universe)) +
  geom_bar(stat = "identity", position = "dodge") + xlab("Proportion of sentiment") + ylab("Sentiment")
```

Both universes heavily use words that imply fear and anger. Marvel uses more fear-related words compared to DC, while DC uses more anger-related words when compared to Marvel. Marvel has more words that relate to trust, sadness and disgust when compared to DC. DC has a significantly higher proportion of words that relate to joy and surprise, when compared to Marvel.